Leadership across 59 traditional cultures: an exploratory analysis

### 2019-12-03 leadership_across_cultures_contexts.Rmd
Edits to first paragraph of conclusion

Our results conform to the characteristics of leaders that are emphasized in the literature on the evolution of leadership and provide broad cross-cultural support for several influential theoretical predictions [for review, see @garfield_evolutionary_2019]. Leaders in the ethnographic record are portrayed as generally prosocial, and serve to resolve conflicts and organize cooperation. Leaders also receive material, social, and reproductive benefits. There is also a "dominant" style of leadership involving physical formidability, fear, and aggression.

>>>>

Leaders in the ethnographic record are portrayed as generally prosocial, serve to resolve conflicts and organize cooperation, and receive material, social, and reproductive benefits. There is also a "dominant" style of leadership involving physical formidability, fear, and aggression. These results conform to the characteristics of leaders that are emphasized in the literature on the evolution of leadership and provide broad cross-cultural support for several influential theories, such as the prestige-dominance model, the collective action model, the service-for-prestige model, and the computational services model [for review, see @garfield_evolutionary_2019].
